Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-11-15 doc/ms.tex
include description of the Noebauer models

\textbf{In \citet{2017MNRAS.472.2787N} the early photometric evolution of Type Ia SNe is explored via a variety of explosion models and detailed radiative-transfer calculations. Specifically, \citet{2017MNRAS.472.2787N} examine 2 Chandrasekhar-mass ($M_\mathrm{Ch}$) explosions and compare their evolution to sub-Chandrasekhar explosions and pure deflagrations. The 2 $M_\mathrm{Ch}$ explosions include the ``W7'' carbon-deflagration model of \citet{1984ApJ...286..644N} and the ``N100'' delayed-detonation model from \citet{2013MNRAS.429.1156S}. The sub-Chandrasekhar models include: a violent WD-WD merger, which triggers a carbon detonation in the more massive WD, a centrally ignited detonation, and a sub-Chandrasehkar double detonation explosion, in which a He-surface-layer detonation triggers a carbon detonation in the WD core. \citet{2017MNRAS.472.2787N} note that, of these last two sub-Chandrasehkar models, the later provides the more realistic scenario. Finally, \citet{2017MNRAS.472.2787N} also examine the ``N5def'' and ``N1600Cdef'' pure deflagrations from \citet{2014MNRAS.438.1762F}.}

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Noebauer.pdf}
  \caption{
  \textbf{Comparison of the models from \citet{2017MNRAS.472.2787N}
  to the \abc\ $g$-band light curve (\textit{top}) and the $(B-V)_0$ color curve (\textit{bottom}). The
  light curve has been corrected for the distance modulus to \abc\
  (\S\ref{sec:host}), while both the light curve and color curve have been
  corrected for reddening. Each light curve is translated to match the LCO
  observations $\sim$1.7\,d after $t_0$ given the uncertain time of explosion.
  Translational offsets are listed in the bottom panel legend, which shows the
  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
  (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
  are shown as dash-dot lines, while PDD models (labeled as PDDEL) are shown
  as dashed lines. The inset in the top panel shows the residuals relative to
  the PDDEL7n model. The PDD models provide a better match to the
  observations.} 
  } \label{fig:noebauer} 
\end{figure}

\textbf{In Figure~\ref{fig:noebauer} we compare photometric observations of
\abc\ to the large-$^{56}$Ni yield DD and PDD models presented in
\citet{2014MNRAS.441..532D}.
}

The detonation of a WD with $M < 1.4 \, M_\odot$, which can occur if triggered by a He-surface-layer detonation (known as the sub-Chandrasekhar double detonation), can produce a rapid rise and early blue optical colors (e.g., \citealt{2017MNRAS.472.2787N}). While this qualitative behavior matches \abc, the $U-V$ colors predicted in \citet{2017MNRAS.472.2787N} do not match our observations. In particular, the sub-Chandrasekhar double detonation model $U - V$ colors rapidly evolve from $\sim$$-0.6\,\mathrm{mag}$ $\sim$1\,d after explosion to $\sim$0.5\,mag $\sim$3\,d after explosion. We observe a steady $U - V$ color evolution from the red to the blue for \abc, however, with $U - V \approx 0.6 \, \mathrm{mag}$ $\sim$2\,d after $t_0$ and $U - V \approx 0 \, \mathrm{mag}$ $\sim$8\,d after $t_0$. As such we conclude that \abc\ is not the result of a sub-Chandrasekhar double detonation. \citet{2017MNRAS.472.2787N} note that their one-dimensional models may not capture the predicted asphericity for sub-Chandrasekhar double detonations, though moving away from the preferred viewing angle results in redder colors and a more gradual rise, which is not observed for \abc.

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
  \caption{
  \textbf{Comparison of the DD and PDD models of \citet{2014MNRAS.441..532D}
  to the \abc\ $g$-band light curve (\textit{top}) and the $(B-V)_0$ color curve (\textit{bottom}). The
  light curve has been corrected for the distance modulus to \abc\
  (\S\ref{sec:host}), while both the light curve and color curve have been
  corrected for reddening. Each light curve is translated to match the LCO
  observations $\sim$1.7\,d after $t_0$ given the uncertain time of explosion.
  Translational offsets are listed in the bottom panel legend, which shows the
  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
  (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
  are shown as dash-dot lines, while PDD models (labeled as PDDEL) are shown
  as dashed lines. The inset in the top panel shows the residuals relative to
  the PDDEL7n model. The PDD models provide a better match to the
  observations.} 
  } \label{fig:dessart} 
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Piro.pdf}
  \caption{  
  \textbf{Same as Figure~\ref{fig:dessart}, featuring models from
  \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni mixing in the SN ejecta
  increases from the short-dash, light lines to the long-dash, dark lines.
  Unlike Figure~\ref{fig:dessart}, each model features the same
  $M_\mathrm{Ni}$, while the model names reflect the boxcar widths used to
  approximate the effects of mixing in the ejecta (see
  \citealt{2016ApJ...826...96P}). The top panel inset shows the
  residuals relative to the $0.25\,M_\odot$ model. The observations are best
  matched by the $0.25\,M_\odot$ model, i.e. the model with the most
  significant mixing.}
  }
  \label{fig:piro}
\end{figure}

>>>>

\textbf{In \citet{2017MNRAS.472.2787N} the early photometric evolution of Type
Ia SNe is explored via a variety of explosion models and detailed
radiative-transfer calculations. Specifically, \citet{2017MNRAS.472.2787N}
examine two Chandrasekhar-mass ($M_\mathrm{Ch}$) explosions and compare their
evolution to sub-Chandrasekhar explosions and pure deflagrations. The
$M_\mathrm{Ch}$ explosions include the ``W7'' carbon-deflagration model of
\citet{1984ApJ...286..644N} and the ``N100'' delayed-detonation model from
\citet{2013MNRAS.429.1156S}. The sub-Chandrasekhar models include: a violent
WD-WD merger, which triggers a carbon detonation in the more massive WD, a
centrally ignited sub-Chandrasehkar detonation, and a sub-Chandrasehkar double
detonation explosion, in which a He-surface-layer detonation triggers a carbon
detonation in the core. \citet{2017MNRAS.472.2787N} note that, of these
last two sub-Chandrasehkar models, the later provides the more realistic
scenario. Finally, \citet{2017MNRAS.472.2787N} also examine the ``N5def'' and
``N1600Cdef'' pure deflagration explosions from \citet{2014MNRAS.438.1762F}.}

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Noebauer.pdf}
  \caption{
%
  \textbf{Comparison of the models from \citet{2017MNRAS.472.2787N} to the
  \abc\ $V$-band light curve (\textit{top}) and the $(B-V)_0$ color curve
  (\textit{bottom}). The light curve has been corrected for the distance
  modulus to \abc\ (\S\ref{sec:host}), while both the light curve and color
  curve have been corrected for reddening. To guide the eye early
  $g_\mathrm{PTF}$ observations are shown as open circles, though we caution
  that \abc\ may exhibit significant color evolution at this phase in which
  case $g_\mathrm{PTF}$ would be a poor proxy for $V$. Each model light curve
  is translated to match the LCO observations $\sim$1.7\,d after $t_0$ given
  the uncertain time of explosion. Translational offsets are listed in the
  bottom panel legend, which shows the models in order of decreasing
  $^{56}$Ni from top to bottom, then left to right. The inset in
  the top panel shows the residuals relative to the W7 model.} }
  \label{fig:noebauer} 
\end{figure}

\textbf{In Figure~\ref{fig:noebauer} we compare photometric observations of
\abc\ to the models presented in
\citet{2017MNRAS.472.2787N}. Interestingly, the sub-Chandrasekhar double detonation model (subChDoubleDet) replicates the early wiggle in the $V$-band light curve. However, this match requires an explosion \textit{after} our initial detection of \abc, \textit{and} extreme color evolution. Thus, the subChDoubleDet model is incompatible with the observations. The sub-Chandrasekhar detonation (subChDet) provides a better match to the observations, though this model is not favored as a particularly realistic scenario (see above). Of the sub-Chandrasekhar models the violent merger model (Merger) provides the best match to the observations including the early rise and color evolution. In detail, however, this model does not match the early wiggles in the light curve, has consistently redder colors than \abc, and requires $t_\mathrm{exp} \approx 2.3$\,d prior to $t_0$. As such, we postulate that \abc\ is not the result of a violent WD-WD merger.}

\textbf{For clarity, of the two pure deflagration models only N5def is shown, however, the evolution of N1600Cdef is very similar. While the pure deflagration models produce the bluest colors at early times, they are underluminous at times $> t_0 + 4\,\mathrm{d}$ and already rapidly evolving towards the red at $\sim$$t_0 + 7$ (\abc\ exhibits a nearly constant $(B-V)_0$ color for $\sim$19\,d after $t_0$). Thus, we conclude that \abc\ is not compatible with pure deflagrations.}

\textbf{Of the $M_\textrm{Ch}$ models, the W7 model better matches the observations as the N100 model features a faster rise and higher luminosity than what is observed. We explore delayed detonation models in further detail below.
}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
  \caption{
  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the DD and PDD models
  from \citet{2014MNRAS.441..532D}. The bottom panel legend lists the models
  in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
  (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
  are shown as dash-dot lines, while PDD models (labeled as PDDEL) are shown
  as dashed lines. The inset in the top panel shows the residuals relative to
  the PDDEL7n model. The PDD models provide a better match to the
  observations.} 
  } \label{fig:dessart} 
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Piro.pdf}
  \caption{  
  \textbf{Same as Figure~\ref{fig:noebauer}, featuring models from
  \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni mixing in the SN ejecta
  increases from the short-dash, light lines to the long-dash, dark lines.
  Unlike Figure~\ref{fig:dessart}, each model features the same
  $M_\mathrm{Ni}$, while the model names reflect the boxcar widths used to
  approximate the effects of mixing in the ejecta (see
  \citealt{2016ApJ...826...96P}). The top panel inset shows the
  residuals relative to the $0.25\,M_\odot$ model. The observations are best
  matched by the $0.25\,M_\odot$ model, i.e. the model with the most
  significant mixing.}
  }
  \label{fig:piro}
\end{figure}
